An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-29 poly-embed-journal/poly-embed-journal.tex
last round before arxiv (?)

%% surrogates are important.  in particular, consistent surrogates. (general intro)
In supervised learning, one tries to learn a hypothesis which fits labeled data as judged by a target loss function.
Unfortunately, minimizing the target loss directly is typically computationally intractable for discrete prediction tasks like classification, ranking, and structured prediction.
Instead, one typically minimizes a surrogate loss which is convex and therefore efficiently minimized.
After learning a surrogate hypothesis, a link function then translates back to the target problem.
To ensure the surrogate and link properly correspond to the target problem, the surrogate must be \emph{consistent}, meaning that minimizing the surrogate loss over enough data will also minimize the target loss.

@@

Using this framework, we give several constructive results to design new consistent surrogates, as well as a suite of tools to analyze existing surrogates.
As a first step, in \S~\ref{sec:poly-loss-embed}, we show that such an embedding scheme is intimately related to the class of \emph{polyhedral} loss functions, i.e., those that are piecewise-linear and convex.
\begin{restatable}{theorem}{embedpolyinformal}\label{thm:embed-poly-main}
  Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
\end{restatable}%\vskip-5pt
\noindent
Crucially, we go on in \S~\ref{sec:calibration} to show that an embedding gives rise to a calibrated link function, and is therefore consistent with respect to the target loss.
\begin{restatable}{theorem}{linkinformal}\label{thm:link-main}
  Given any polyhedral loss $L$, let $\ell$ be a discrete loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
\end{restatable}
\noindent
Beyond consistency, we show in \S~\ref{subsec:regret-bounds} that any polyhedral surrogate achieves a linear surrogate regret bound, which allows one to translate generalization bounds from the surrogate to the target.
Our results are constructive: given a discrete target loss, we show how to define a surrogate and construct a calibrated link, and given a polyhedral surrogate, we show how to find a target loss that it embeds.

@@

Finally, we also provide several observations beyond what is needed to prove our main results, which we view as conceptual contributions (\S~\ref{sec:min-rep-sets},~\ref{sec:poly-ie-consistency}).
Using tools from property elicitation, we show an equivalence between minimum representative sets (those of minimum cardinality) and ``non-redundancy'', wherein no report is dominated by another.
We further show that, while the minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
The paper concludes with an interesting observation (Theorem~\ref{thm:poly-ie-implies-consistent}): while indirect property elicitation is generally a strictly weaker condition than consistency, the two are equivalent when restricting to the class of polyhedral surrogates.

Taken together, we view our contributions as both conceptual and practical.
We uncover the remarkable structure of polyhedral surrogates, deepening our understanding of the relationship between surrogate and discrete target losses.
This structure leads to a powerful new framework to design and analyze surrogate losses.
As we illustrate with several examples, this framework has already been applied to solve open questions by designing new surrogates, to uncover the behavior of existing surrogates, and to construct link functions in complex structured problems.
We conclude with several exciting directions for future work.

@@

In this work, we introduce an embedding framework to design and analyze consistent convex and surrogates for discrete prediction tasks.
Our results are constructive; as we outline in \S~\ref{sec:applications}, they can be fruitfully applied to a range of tasks, from designing new surrogates and link functions to understanding the consistency or inconsistency of existing surrogates.
Beyond these tools, our results shed light on fundamental questions about the design of consistent surrogates.

@@

In previous work, we introduce and present some bounds for embedding dimension
based on optimality conditions \citep{finocchiaro2020embedding}\raft{Thoughts on using 1st person plural here for previous work?  It is the same authors, and same broader project... I think it's less awkward this way, but I'm okay with 3rd person too}\jessie{So long as we're submitting to a single-blind venue, I'm fine with it.}.
We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these numbers may always be the same.
It is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
Moreover, beyond the fact that the embedding dimension upper bounds convex elicitation complexity, it remains to understand the relationship between these two quantities in dimensions greater than~$1$.

@@

\paragraph{Polyhedral vs.\ smooth surrogates}
The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
In practice, minimizing such surrogates often corresponds to learning the entire underlying data distribution and compute the desired target task with the full distribution in hand.
However, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
While generalization rates may suffer for nonsmooth losses, polyhedral surrogates achieve linear regret transfer bounds (\S~\ref{subsec:regret-bounds}), so the target generalization rates may remain the same; see also~\citet{frongillo2021surrogate}.
Even further, \citet{lapin2016loss} suggest that optimizing a nonsmooth loss that directly captures the target problem of interest, rather than a smooth one that implicitly fits to the entire underlying distribution, can improve performance in limited data settings.
We would like to verify this intuition, with specific cases or broad results comparing smooth and polyhedral losses.
  % \raf{Show that polyhedral losses are ``more efficient'' in a statistical sense?
  % See references recommended by Peter Bartlett.}
%Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.

@@

Finally, recall that we motivated the idea of an embedding as a way to ``convexify'' a discrete loss.
It is not clear, however, how embeddings relate to the convex envelope operation, which is perhaps the most direct way to perform this convexification given the map $\varphi$.
For example, suppose $L:\reals^d\to\reals^\Y_+$ embeds $\ell:\R\to\reals^\Y_+$ via the embedding $\varphi:\R\to\reals^d$, and consider the (polyhedral) surrogate $L':\reals^d\to\reals^\Y_+$ given by $L'_y = (L_y + \ones_{\varphi(\R)})^{**}$, where here $\ones$ denotes the convex indicator and $(\cdot)^{**}$ the biconjugate.
(One might also consider similar operations that keep $L'$ finite-valued.)
When it the case that $L'$ also embeds $\ell$?
Conversely, we would like to know when the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} can be viewed as a convex envelope.

@@

\begin{definition}[Supports]
	%A halfspace $H^+$ is \emph{valid} for $P$ if $P \subseteq H^+$.
	\jessiet{Removed valid as it doesn't come up later.  \# burn}
	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
	% (i) $P \subseteq H^+$ for a halfspace $H^+$ corresponding to $H$
	(i) $P \subseteq H^+$ for a halfspace $H^+$ with $H = \partial H^+$, and
	(ii) $H \cap \partial P \neq \emptyset$.
	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \partial P$.
\end{definition}

@@

\begin{claim}\label{claim:extended-poly-risk-poly}
	For any minimizable function $L$ such that $\risk L$ is polyhedral, its extension $\risk L_+$ is also polyhedral.
\end{claim}
\begin{proof}
  We will think of $\risk L$ as defined $\risk L:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(\risk L) = \simplex$.
For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
If $p \not \in \simplex$, then $\risk L(p) = -\infty$.
Moreover, since $\risk L$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written
\newcommand{\B}{\mathcal{B}} 
\begin{align*}
\risk L(p) 
&= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
&= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)\\
&= \min_{(b, \beta) \in \B} \inprod{p}{b - \ones \beta} - \delta(p \mid \simplex)~,
\end{align*}
where $\B = \{(b_i, \beta_i)\}_{i = 1}^k$ from the second line.
For any $x \in \reals^\Y_+$, consider its normalization $\bar x$ with $(\bar x)_i = \frac{x_i}{\|x\|_1}$ such that $\bar x \in \simplex$.
As $\risk L_+$ is the $1$-homogeneous extension of $\risk L$, we observe $\risk L(x)_+ = \risk L(\bar x)$ for all $x \in \reals^\Y_+$.
Therefore, we have $\risk L_+(x) = \risk L(\bar x) = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$, which is polyhedral as the pointwise min over a finite set of linear functions.
\raft{You have to connect the display to the conclusion; one way is to write out what $\risk L_+$ is, but you have to justify it either way.}
\end{proof}

@@

\lemmaX*
\begin{proof}
	%\jessiet{Get to Assumption~\ref{assum:V-star-exists-infinite} quickly}
%As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
%\jessie{$\risk L$ to $\risk L_+$.  Change Claim 6: if you have a minimizable loss and $\risk L$ is polyhedral, then $\risk L_+$ is polyhedral.}
Since $\risk L$ is polyhedral, so is $\risk L_+$ by Claim~\ref{claim:extended-poly-risk-poly}.
Therefore, we have satisfied the requirements of Proposition~\ref{prop:poly-risk-assumption-satisfied}, and can conclude there is a $\V^*$ such that $\risk L_+ = g_{\V^*}$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
Moreover, there must be a finite set $\R^*$ such that $\V^* = L(\R^*)$ by construction. %, which is representative as $\risk L = \min_{v \in \V^*}\inprod{p}{v} - \delta\{p \mid \simplex\} = \min_{v \in L(\R^*)}\inprod{p}{v} - \delta\{p \mid \simplex\}$.
For all $p \in \simplex$, there is a $v \in \V^* = L(\R^*)$ and $r \in \R^*$ such that $v = \risk L(p) = L(r)$ and therefore $r \in \prop{L}(p)$ as $L$ is minimizable.
As this is true for all $p \in \simplex$, $\R^*$ is representative for $L$. \raft{``generates the Bayes risk'' not defined; need to slow down here I think and find the rigorous statement among the many things you proved! \jessie{Had a feeling this comment was coming when I wrote it.  :grimace: burn if okay now}}.
%Since $\risk L$ is polyhedral and concave there exists a finite set $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.
%Moreover as $\V$ is finite, $g_{\V} = \risk L_+$ (by $1$-homogeneity following from the form of $g_{\V}$) is also polyhedral and concave, and $f_\V = g_\V$ on $\simplex$.
%Therefore, there is a $\V^* \subseteq \V$ such that $L$ and $\V^*$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.
%Moreover, any set $\R$ such that $\V^* = L(\R)$ is a finite representative set for $L$, and such a set must exist by the existence and construction of $\V^*$.
%%Given the form of $\risk L$ written as a pointwise max of finitely many affine functions (which are loss vectors) in $\V$, the loss $L$ has a finite representative set. 
%%Moreover, by Claim~\ref{claim:gV-and-fV}, $g_\V = f_\V$ on the simplex.

>>>>

%% surrogates are important.  in particular, consistent surrogates. (general intro)
In supervised learning, one tries to learn a hypothesis which fits labeled data as judged by a target loss function.
Minimizing the target loss directly is typically computationally intractable for discrete prediction tasks like classification, ranking, and structured prediction.
Instead, one typically minimizes a surrogate loss which is convex and therefore efficiently minimized.
After learning a surrogate hypothesis, a link function then translates back to the target problem.
To ensure the surrogate and link properly correspond to the target problem, the surrogate must be \emph{consistent}, meaning that minimizing the surrogate loss over enough data will also minimize the target loss.

@@

Using this framework, we give several constructive results to design new consistent surrogates, as well as a suite of tools to analyze existing surrogates.
As a first step, in \S~\ref{sec:poly-loss-embed}, we show that such an embedding scheme is intimately related to the class of \emph{polyhedral} loss functions, i.e., those that are piecewise-linear and convex.
\begin{restatable}{theorem}{embedpolyinformal}\label{thm:embed-poly-main}
  Every discrete loss $\ell$ is embedded by some polyhedral loss $L$, and every polyhedral loss $L$ embeds some discrete loss $\ell$.
\end{restatable}%\vskip-5pt
\noindent
Crucially, we go on in \S~\ref{sec:calibration} to show that an embedding gives rise to a calibrated link function, and is therefore consistent with respect to the target loss.
\begin{restatable}{theorem}{linkinformal}\label{thm:link-main}
  Given any polyhedral loss $L$, let $\ell$ be a discrete loss it embeds. There exists a link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
\end{restatable}
\noindent
Beyond consistency, we show in \S~\ref{subsec:regret-bounds} that any polyhedral surrogate achieves a linear surrogate regret bound, which allows one to translate generalization bounds from the surrogate to the target.
Our results are constructive: given a discrete target loss, we show how to define a surrogate and construct a calibrated link, and given a polyhedral surrogate, we show how to find a discrete loss that it embeds.

@@

Finally, we also provide several observations beyond what is needed to prove our main results, which we view as conceptual contributions (\S~\ref{sec:min-rep-sets},~\ref{sec:poly-ie-consistency}).
Using tools from property elicitation, we show an equivalence between minimum representative sets (those of minimum cardinality) and ``non-redundancy'', wherein no report is dominated by another.
We further show that, while a minimum representative set is not always unique, the loss values associated with it are unique, giving rise to a natural ``trim'' operation on losses.
The paper concludes with an interesting observation (Theorem~\ref{thm:poly-ie-implies-consistent}): while indirect property elicitation is generally a strictly weaker condition than consistency, the two are equivalent when restricting to the class of polyhedral surrogates.

Taken together, we view our contributions as both conceptual and practical.
We uncover the remarkable structure of polyhedral surrogates, deepening our understanding of the relationship between surrogate and discrete target losses.
This structure leads to a powerful new framework to design and analyze surrogate losses.
As we illustrate with several examples, this framework has already been applied to solve open questions by designing new surrogates, to uncover the behavior of existing surrogates, and to construct link functions in complex structured problems.
We conclude with several directions for future work.

@@

In this work, we introduce an embedding framework to design and analyze consistent, convex surrogates for discrete prediction tasks.
Our results are constructive; as we outline in \S~\ref{sec:applications}, they can be fruitfully applied to a range of tasks, from designing new surrogates and link functions to understanding the consistency or inconsistency of existing surrogates.
Beyond these tools, our results shed light on fundamental questions about the design of consistent surrogates.

@@

In previous work, we introduce and present some bounds for embedding dimension
based on optimality conditions \citep{finocchiaro2020embedding}\raft{Thoughts on using 1st person plural here for previous work?  It is the same authors, and same broader project... I think it's less awkward this way, but I'm okay with 3rd person too}\jessie{So long as we're submitting to a single-blind venue, I'm fine with it.}.
We show in particular that a target loss has embedding dimension $1$ if and only if it hase convex elicitation complexity $1$, underscoring the possibility that these quantities may be the same for all discrete losses.
It is unclear if these bounds are tight or if they can be improved by leveraging information about adjacent level sets of an embedded property.
Moreover, beyond the fact that the embedding dimension upper bounds convex elicitation complexity, it remains to understand the relationship between these two quantities in dimensions greater than~$1$.

@@

\paragraph{Polyhedral vs.\ smooth surrogates}
The literature on convex surrogates focuses mainly on smooth surrogate losses~\citep{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite,menon2019multilabel,zhang2020convex,bao2020calibrated}.
In practice, minimizing such surrogates often implicitly fits a model to the full conditional label distributions.
On the other hand, \citet[Section 1.2]{ramaswamy2018consistent} contend that optimizing nonsmooth losses may enable reduction of the prediction dimension while maintaining consistency relative to smooth losses, improving downstream efficiency of the learning algorithm.
While generalization rates may suffer for nonsmooth losses, polyhedral surrogates achieve linear regret transfer bounds (\S~\ref{subsec:regret-bounds}), so the target generalization rates may remain the same; see also~\citet{frongillo2021surrogate}.
Even further, \citet{lapin2016loss} suggest that optimizing a nonsmooth loss that directly captures the target problem of interest, rather than a smooth one that implicitly fits to the full conditional label distributions, can improve performance in limited data settings.
We would like to verify this intuition, with specific cases or broad results comparing smooth and polyhedral losses.
  % \raf{Show that polyhedral losses are ``more efficient'' in a statistical sense?
  % See references recommended by Peter Bartlett.}
%Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems~\citep{yang2018consistency,yu2018lovasz,lapin2015top}.

@@

Finally, recall that we motivated the idea of an embedding as a way to ``convexify'' a discrete loss.
It is not clear, however, how embeddings relate to the convex envelope operation, which is perhaps the most direct way to perform this convexification given the map $\varphi$.
For example, suppose $L:\reals^d\to\reals^\Y_+$ embeds $\ell:\R\to\reals^\Y_+$ via the embedding $\varphi:\R\to\reals^d$, and consider the (polyhedral) surrogate $L':\reals^d\to\reals^\Y_+$ given by $L'_y = (L_y + \ones_{\varphi(\R)})^{**}$, where here $\ones$ denotes the convex indicator and $(\cdot)^{**}$ the biconjugate.
(One might also consider similar operations that keep $L'$ finite-valued.)
When is it the case that $L'$ also embeds $\ell$?
Conversely, we would like to know when the construction in Theorem~\ref{thm:discrete-loss-poly-embeddable} can be viewed as a convex envelope.

@@

\begin{definition}[Supports]
	%A halfspace $H^+$ is \emph{valid} for $P$ if $P \subseteq H^+$.
	A hyperplane $H$ \emph{supports} the polyhedron $P$ if 
	% (i) $P \subseteq H^+$ for a halfspace $H^+$ corresponding to $H$
	(i) $P \subseteq H^+$ for a halfspace $H^+$ with $H = \partial H^+$, and
	(ii) $H \cap \partial P \neq \emptyset$.
	Moreover, $H$ supports $P$ at $x$ if $x \in H \cap \partial P$.
\end{definition}

@@

\begin{claim}\label{claim:extended-poly-risk-poly}
	For any minimizable function $L$ such that $\risk L$ is polyhedral, its extension $\risk L_+$ is also polyhedral.
\end{claim}
\begin{proof}
  We will think of $\risk L$ as defined $\risk L:\reals^\Y\to\reals_+\cup\{-\infty\}$  with $\dom(\risk L) = \simplex$.
For $p \in \simplex$, we know $\sum_i p_i = 1$, and can write any inner product $\inprod{p}{b} - \beta = \inprod{p}{b} - \inprod{p}{\beta \ones} = \inprod{p}{b - \beta \ones}$.
If $p \not \in \simplex$, then $\risk L(p) = -\infty$.
Moreover, since $\risk L$ is polyhedral, it is finitely generated \citep[Proposition 19.1.2]{rockafellar1997convex} and can be written
\newcommand{\B}{\mathcal{B}} 
\begin{align*}
\risk L(p) 
&= \min(\inprod{p}{b_1} - \beta_1, \ldots, \inprod{p}{b_k} - \beta_k) - \delta(p \mid \simplex)\\
&= \min(\inprod{p}{b_1 - \beta_1 \ones}, \ldots, \inprod{p}{b_k - \beta_k \ones}) - \delta(p \mid \simplex)\\
&= \min_{(b, \beta) \in \B} \inprod{p}{b - \ones \beta} - \delta(p \mid \simplex)~,
\end{align*}
where $\B = \{(b_i, \beta_i)\}_{i = 1}^k$ from the second line.
For any $x \in \reals^\Y_+$, consider its normalization $\bar x$ with $(\bar x)_i = \frac{x_i}{\|x\|_1}$ such that $\bar x \in \simplex$.
As $\risk L_+$ is the $1$-homogeneous extension of $\risk L$, we observe $\risk L(x)_+ = \risk L(\bar x)$ for all $x \in \reals^\Y_+$.
Therefore, we have $\risk L_+(x) = \risk L(\bar x) = \min_{(b, \beta) \in \B} \inprod{\bar x}{b - \ones \beta}$, which is polyhedral as the pointwise min over a finite set of linear functions.
\raft{Error in the conversion to $\risk L_+$: I think you need to multiply by $\|x\|_1$.  But maybe an easier route is to simply replace the $\delta(p \mid \simplex)$ with $\delta(x \mid \reals^\Y_+)$ and observe that (a) the result is 1-homogenous, and (b) agrees with $\risk L$ on $\simplex$, ergo, must be its 1-homog extension.}
\end{proof}

@@

\lemmaX*
\begin{proof}
	%\jessiet{Get to Assumption~\ref{assum:V-star-exists-infinite} quickly}
%As in this appendix, we consider $\V = L(\R)$ such that $g_\V = \risk L_+$.
%\jessie{$\risk L$ to $\risk L_+$.  Change Claim 6: if you have a minimizable loss and $\risk L$ is polyhedral, then $\risk L_+$ is polyhedral.}
Since $\risk L$ is polyhedral, so is $\risk L_+$ by Claim~\ref{claim:extended-poly-risk-poly}.
Therefore, we have satisfied the requirements of Proposition~\ref{prop:poly-risk-assumption-satisfied}, and can conclude there is a finite set $\V^*\subseteq L(\R)$ such that $\risk L_+ = g_{\V^*}$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
Hence, there is a finite set $\R^*$ such that $\V^* = L(\R^*)$. %, which is representative as $\risk L = \min_{v \in \V^*}\inprod{p}{v} - \delta\{p \mid \simplex\} = \min_{v \in L(\R^*)}\inprod{p}{v} - \delta\{p \mid \simplex\}$.
For all $x\in\reals^\Y_+$, there exists $v \in \V^*$ such that $\inprod{v}{x} = g_{\V^*}(x)$, and thus some $r\in\R^*$ such that $\inprod{L(r)}{p} = g_{\V^*}(x)$.
Thus, for all $p \in \simplex$, there exists $r \in \R^*$ such that $\risk L(p) = \risk L_+(p) = g_{\V^*}(p) = \inprod{L(r)}{p}$ and therefore $r \in \prop{L}(p)$\raft{Edited and fleshed out}.
As this is true for all $p \in \simplex$, $\R^*$ is representative for $L$.
%Since $\risk L$ is polyhedral and concave there exists a finite set $\V$ such that $\risk L = f_\V$ by Claim~\ref{claim:f-min-affine}.
%Moreover as $\V$ is finite, $g_{\V} = \risk L_+$ (by $1$-homogeneity following from the form of $g_{\V}$) is also polyhedral and concave, and $f_\V = g_\V$ on $\simplex$.
%Therefore, there is a $\V^* \subseteq \V$ such that $L$ and $\V^*$ satisfy Assumption~\ref{assum:V-star-exists-infinite} by Proposition~\ref{prop:poly-risk-assumption-satisfied}.
%Moreover, any set $\R$ such that $\V^* = L(\R)$ is a finite representative set for $L$, and such a set must exist by the existence and construction of $\V^*$.
%%Given the form of $\risk L$ written as a pointwise max of finitely many affine functions (which are loss vectors) in $\V$, the loss $L$ has a finite representative set. 
%%Moreover, by Claim~\ref{claim:gV-and-fV}, $g_\V = f_\V$ on the simplex.
